Crossing Origins by Crossing Formats

### 2012-11-22 main.tex
edits in Section 2

\documentclass[10pt, conference, compsocconf]{IEEEtran}

@@

@@

\begin{IEEEkeywords}
Web Security; Polyglot; Injection; Cross-domain.
\end{IEEEkeywords}

@@

@@

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the \emph{Same-Origin Policy}. We begin by 
generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the Same-Origin Policy (SOP). 
The SOP dictates that a two document can only access each others 
content and resources if they share the same origin. Similarly this applies to communication as 
well; a document can only directly communicate with the server from which it originated. 
This is not to be confused with Cross-Origin Resource Sharing (CORS), which is an 
intentional relaxing of the SOP.

@@

Other examples of problematic elements include the object- and embed-tags. These 
tags allow inclusion of resources that might require a 
plug-in to run. As with images, the content handled by the plug-in retains its origin, 
but the browsers are forced to rely on the plug-ins to employ correct security 
measures to prevent information leaks. While the containing page is restricted 
from directly accessing the content handled by the plug-in, a number of plugins provide 
an API for interacting with the plug-in and the data. As we will show, this can easily lead to 
to cross-origin information leaks.

@@

A polyglot is defined as ``A person who knows several languages.'', and the term
is widely used in various fields of science. In computer science, a polyglot is
a program that is valid in multiple programming languages. In this paper we use
a broader definition of a programming language, not limited to code meant for
compilation to machine code or scripting languages, but extended to any format
that requires interpretation before rendering.

@@

\paragraph{Malicious polyglots}

@@

A malicious polyglot is composed of two formats where one is benign in nature and the other
contains a malicious payload. 
% Characteristics of a malicious polyglot
The benign format would preferably be a widely accepted format with the capability 
of hiding arbitrary data, e.g. an image with comment fields. The malicious file 
format would ideally have strong capabilities, s
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the expected run-time context and the actual context it is executed in. 
In the expected context the content would be interpreted as the 
benign format. In the actual context, however, the content is coerced to be 
interpreted as the malicious format containing the payload.

Even if a verification process exists, it would verify that the content is valid 
in the expected context. Due to the nature of the polyglot, the content would be 
verified as valid and benign, but subsequently the malicious
content is executed.

In a web context, coercing content to be interpreted as a different type be 
done easily. If the content is loaded using an image-tag it will be interpreted 
as an image, if a script-tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.

@@

The target in this scenario is a user of the vulnerable website. The polyglot is
served in the benign format on the vulnerable server. While the user is logged in to
the service that the vulnerable website provides, the user unsuspectingly visits
the attackers malicious website. The page embeds the polyglot content, but
coerces the browser to interpret the content as the malicious format. 
How  on the capabilities of the malicious format, 
The attacker can now
exploit the vulnerability, either by making requests to the vulnerable website
in the context of the user; or by extracting information about the user that is
stored on the vulnerable website.

@@

%The same-origin policy is intended to prevent a document from one origin from
%accessing the content of a document of another origin. 
As an example the
same-origin policy allows a script-tag in one document to include JavaScript of
another origin and execute it in the context of that document. If an attacker is
able to inject an HTML document with JavaScript syntax in such a way that it
became valid JavaScript, the attacker could include the document across origins
via a script-tag and extract its content, thereby circumventing the same-origin
policy.

@@

%By requesting the site with parameter $guess=</body></html>;x=<html><body>$,
%the resulting document, 
The document in listing \ref{lst:html-js}, is both
malformed but valid HTML and valid JavaScript in browsers that support E4X. The
document can be included as a script in another document and the secret can be
extracted from variable x. This implies that if an attacker is able to inject
HTML syntax into a document, such that the result is two balanced E4X trees,
then information can be extracted across origins.

\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot]
<html><body>
Hello </body></html>;x=<html><body>!
Your secret is 'safe with me'.
</body></html>
\end{lstlisting}

This attack has been suggested as a potential way to bypass Content Security
Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
engine, used in Firefox, this limits the exploitability of this example. While
this is an unlikely scenario using JavaScript as the injected format, section
\ref{sec:vuln} will show how this can be achieved in practice.

% Description of attack technique 
A content repurposing attack targets the users of a website
that allows and serves user supplied files. This could be a file sharing
service, an image database, or a job search service. The service would only 
accept a limited set of file-types, and the files are verified to
be of one of these types, e.g. an image, before being served to the end
user. By submitting a polyglot to such a service, an attacker can trick the
service into serving malicious content under the origin of the service. The
service will verify the file, assuming that it is of the benign format, but once
the content is served an attacker can coerce the content to be interpreted as
the malicious format.

@@

%3 pages 
\section{Vulnerabilities}
\label{sec:vuln}

@@

Preventing syntax injection attacks on the server-side poses severe challenges.
Even server-side filtering of HTML syntax to prevent cross-side scripting
attacks has proved difficult due to the many contexts in which JavaScript can be 
introduced. Filtering all potentially harmful tokens from all formats in which a 
document could be interpreted, will likely be near impossible.

@@

Traditionally, browser vendors have allowed the browser to override the 
MIME-type provided by the server for compatibility reasons. This is a compromise 
to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
has repeatedly shown to lead to security issues. The affected browser vendors 
could help mitigate this problem by limiting the ways content can be coerced to be 
interpreted as a particular format.

In the case of PDF-based polyglots, the browser could intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the object tag. By acknowledging that there could be a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat, the vulnerability could be mitigated.

One could argue that the browser is as confused as the originating server as to the 
actual format of the content, and that the issue would be best resolved by the 
corresponding plug-in.

@@

As a general rule of thumb, the interpreter at the very least alert the user if the served 
content-type differs from the expected. A preferred alternative would be to 
not attempt to interpret the content at all. This holds true especially when 
the served content-type is well known and radically different from that which 
the interpreter is designed for.

As for the PDF file format, the underlying design decisions has led to the 
current parsing being very relaxed, even with respect to the specification. 
Making the parsing more strict and enforcing many of the specified requirements 
would greatly reduce the attack surface. It is, however, not a complete 
mitigation approach. Since the PDF format is a container format it is designed to 
embed syntax from other files. Even when parsing strictly according to 
the specification, it would be a simple task to create a PDF-based polyglot.

@@

%1-2 pages 
\bibliographystyle{IEEEtran}
\bibliography{literature}

>>>>

\documentclass{acm_proc_article-sp}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}

@@

\usepackage{amssymb}
\usepackage[usenames]{color}
\definecolor{lightred}{rgb}{1,0.8,0.8}
\newcommand{\todo}[1]{\colorbox{red}{\textcolor{white}{\sffamily\bfseries\scriptsize TODO}} \textcolor{red}{#1} \textcolor{red}{$\blacktriangleleft$}}

@@

% \begin{IEEEkeywords}
% Web Security; Polyglot; Injection; Cross-domain.
% \end{IEEEkeywords}

@@

\todo{Define SOP}

@@

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the Same-Origin Policy. We begin by 
generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

@@

By crossing origins we mean being able to request and access content
which is normally restricted under the Same-Origin Policy. 
Recall that SOP dictates that a two document can only access each others 
content and resources if they share the same origin. Similarly this applies to communication as 
well; a document can only directly communicate with the server from which it originated. 
This is not to be confused with Cross-Origin Resource Sharing (CORS), which is an 
intentional relaxing of the SOP.

@@

Other examples of problematic elements include the object- and embed-tags. These 
tags allow inclusion of resources that might require a 
plug-in to run. As with images, the content handled by the plug-in retains its origin, 
but the browsers are forced to rely on the plug-ins to employ correct security 
measures to prevent information leaks. While the containing page is restricted 
from directly accessing the content handled by the plug-in, a number of plugins provide 
an API for interacting with the plug-in and the data. As we will show, this can lead to 
to cross-origin information leaks.

@@

A polyglot is defined as ``A person who knows several languages.'', and the term
is widely used in various fields of science. In computer science, a \emph{polyglot} is
a program that is valid in multiple programming languages. In this paper we use
a broader definition of a programming language, not limited to code meant for
compilation to machine code or scripting languages, but extended to any format
that requires interpretation before rendering.

@@

%\paragraph{Malicious polyglots}

@@

A malicious polyglot is composed of two formats where one is benign in nature and the other
contains a malicious payload. 
% Characteristics of a malicious polyglot
The benign format is a widely accepted format with the capability 
of hiding arbitrary data, e.g. an image with comment fields. The malicious 
format has additional capabilities, such as scripting.
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the expected run-time context and the actual context it is executed in. 
In the expected context the content is interpreted as the 
benign format. In the actual context, however, the content is coerced to be 
interpreted as the malicious format containing the payload.

Even if a verification process exists, it verifies that the content is valid 
in the expected context. Due to the nature of the polyglot, the content is 
verified as valid and benign, but subsequently the malicious
content is executed.

In a web context, coercing content to be interpreted as a different type be 
done easily. If the content is loaded using an image-tag it will be interpreted 
as an image, if a script-tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.
\todo{explain the issues and cite Barthe et al.}

@@

\todo{diagram}
The target in this scenario is a user of the vulnerable website. The polyglot is
served in the benign format on the vulnerable server. While the user is logged in to
the service that the vulnerable website provides, the user unsuspectingly visits
the attackers malicious website. The page embeds the polyglot content, but
coerces the browser to interpret the content as the malicious format. 
The capabilities of the malicious format determine the severity of the consequences.
The attacker can
exploit the vulnerability, either by making requests to the vulnerable website
in the context of the user; or by extracting information about the user that is
stored on the vulnerable website.

@@

%The same-origin policy is intended to prevent a document from one origin from
%accessing the content of a document of another origin. 
As an example the
same-origin policy allows a script-tag in one document to include JavaScript of
another origin and execute it in the context of that document. If an attacker is
able to inject an HTML document with JavaScript syntax in such a way that it
became valid JavaScript, the attacker can include the document across origins
via a script-tag and extract its content, thereby circumventing the same-origin
policy.

@@

%By requesting the site with parameter $guess=</body></html>;x=<html><body>$,
%the resulting document, 
The document in Listing \ref{lst:html-js}, is both
malformed but valid HTML and valid JavaScript in browsers that support
EcmaScript for XML (E4X). \todo{ref}

The
document can be included as a script in another document and the secret can be
extracted from variable x. 
This implies that if an attacker is able to inject
HTML syntax into a document, closing all previously open tags and
opening all subsequently closed tags,
then information can be extracted across origins.
The injected HTML in the listing is illustrated by highlighting.

\definecolor{lightgray}{gray}{.8}
\begin{lstlisting}[label=lst:html-js, caption=HTML / E4X Polyglot, escapechar=*]
<html><body>
Hello *\colorbox{lightgray}{$<$/body$><$/html$>$;x=$<$html$><$body$>$}*!
Your secret is 'safe with me'.
</body></html>
\end{lstlisting}

This attack has been suggested as a potential way to bypass Content Security
Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
engine, used in Firefox, this limits the exploitability of this example. However,
this is an unlikely scenario to use JavaScript as the injected format
because HTML characters are typically escaped by content
filters. 
Instead,
Section
\ref{sec:vuln} will show practical attacks based on other formats.

\todo{Mention and explain known attack instances}

\subsection{Content repurposing}
\todo{diagram}
% Description of attack technique 
A content repurposing attack targets the users of a website
that allows and serves user supplied files. Examples are a file sharing
service, an image database, or a job search service. Such a service 
accepts a limited set of file-types, and the files are verified to
be of one of these types, e.g. an image, before being served to the end
user. By submitting a polyglot to such a service, an attacker can trick the
service into serving malicious content under the origin of the service. The
service will verify the file, assuming that it is of the benign format, but once
the content is served an attacker can coerce the content to be interpreted as
the malicious format.

@@

% Scenarios
\todo{Mention and explain known attack instances}

%3 pages 
\section{Vulnerabilities and attacks}
\label{sec:vuln}

@@

Preventing syntax injection attacks on the server-side poses severe challenges.
Even server-side filtering of HTML syntax to prevent cross-side scripting
attacks has proved difficult due to the many contexts in which JavaScript can be 
introduced. Filtering all potentially harmful tokens from all formats in which a 
document may be interpreted is hardly possible.

@@

Traditionally, browser vendors have allowed the browser to override the 
MIME-type provided by the server for compatibility reasons. This is a compromise 
to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
has repeatedly shown to lead to security issues. The affected browser vendors 
can help mitigate this problem by limiting the ways content can be coerced to be 
interpreted as a particular format.

In the case of PDF-based polyglots, the browser can intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the object tag. By acknowledging that there can be a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat, the vulnerability can be mitigated.

One may argue that the browser is as confused as the originating server as to the 
actual format of the content, and that the issue would be best resolved by the 
corresponding plug-in.

@@

As a general rule of thumb, the interpreter at the very least alert the user if the served 
content-type differs from the expected. A preferred alternative is to 
not attempt to interpret the content at all. This holds true especially when 
the served content-type is well known and radically different from that which 
the interpreter is designed for.

As for the PDF file format, the underlying design decisions has led to the 
current parsing being very relaxed, even with respect to the specification. 
Making the parsing more strict and enforcing many of the specified requirements 
will reduce the attack surface. It is, however, not a complete 
mitigation approach. Since the PDF format is a container format it is designed to 
embed syntax from other files. Even when parsing strictly according to 
the specification, it is a simple task to create a PDF-based polyglot.

@@

%1-2 pages 
\bibliographystyle{plain}
\bibliography{literature}

\newpage
\section*{Todo}
Test page
